---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
library(ggplot2)
```

```{css}
body {
  background-color: #fcf6f2;
}
.title {
  margin-bottom: 0;
}
.subtitle {
  margin-top: 0;
  margin-bottom:20px;
  font-style: italic;
}


a, p {
  font-size: 21px;
}

a {
  text-decoration: underline;
}

h1, h3, h4 {
  margin-left: 30px;
}

h2 {
  background-color: #ffdbd1;
  margin: 24px 0;
  padding: 16px 30px;
}

.main-container {
  width: 100%;
  padding: 0;
  max-width: none;
}


pre, p{
  margin-left: 70px;
  margin-right: 70px;
}
```

## Sender and Frequency of SNS messages over time

This is a dynamic report on the data collected from the Frequency & Types of SNS messages survey, click [here]("https://forms.gle/7BLzLQNj7XLEepk87") to open the Google Form and fill in the survey!


## bar graph 1 (SNS message total from friends & acquaintances, by day)

```{r}
#reading the data from online csv url
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTha3xy_SPWUq7wyVxgjkxSeUkbA8oaStoGu0foB2uPxyza95C-UIgCCAbexEEKkOFDtnlk8H2dQ8AT/pub?output=csv")

#cleaning up the data frame for readability (rename variables)
latest_data <- logged_data %>% rename(friends_acquaintances = 2,
                                      family_partner = 3,
                                      morning_msg_from_friends_acquaintances = 4,
                                      midday_msg_from_friends_acquaintances = 5,
                                      night_msg_from_friends_acquaintances = 6,
                                      morning_msg_from_family_partner = 7,
                                      midday_msg_from_family_partner = 8,
                                      night_msg_from_family_partner = 9,)
#cleaning up the data frame for readability (converting all NA entries to 0)
latest_data[is.na(latest_data)] = 0

friends_max <- latest_data[4:6] %>% max() 
# 4th to 6th column of the data frame are the 3 different time frames
# for data collected on friends & acquaintances messages, find the max
# value
family_max <- latest_data[7:9] %>% max()
# 7th to 9th column of the data frame are the 3 different time frames
# for data collected on family & partner messages, find the max
# value

# sum of the number of messages received from all time frames per day
entire_day_from_friends <- latest_data$night_msg_from_friends_acquaintances +  latest_data$midday_msg_from_friends_acquaintances + latest_data$morning_msg_from_friends_acquaintances
entire_day_from_family <- latest_data$night_msg_from_family_partner + latest_data$midday_msg_from_family_partner + latest_data$morning_msg_from_family_partner

# sum of the number of messages received from all time frames per day
day_max_from_friends <- entire_day_from_friends %>% max()
day_max_from_family <- entire_day_from_family %>% max()

# bar graph 1 (SNS message total from friends & acquaintances, by day)
latest_data %>%
  ggplot() +
  geom_bar(aes(x = entire_day_from_friends),
           fill = "red") + 
  labs(title = "Total SNS messages received from friends & acquaintances each day",
       caption = "Source: Google Form survey",
       x = "No. of msg received",
       y = "Observation count")
```

The highest number of SNS messages received from friends & acquaintances in a whole day is `r day_max_from_friends`.

The highest number of SNS messages received from friends & acquaintances during 
any time frame of the day is `r friends_max`.


## bar graph 2 (SNS message total from family & partner, by day)
```{r}
# bar graph 2 (SNS message total from family & partner, by day)
latest_data %>%
  ggplot() +
  geom_bar(aes(x = entire_day_from_family),
           fill = "blue") + 
  labs(title = "Total SNS messages received from family & partner each day",
       caption = "Source: Google Form survey",
       x = "No. of msg received",
       y = "Observation count")
```

The highest number of SNS messages received from family & partner in a whole day is `r day_max_from_family`.

The highest number of SNS messages received from family & partner during any time 
frame of the day is `r family_max`.

## bar graph 3 (Summary and comparison for average SNS messages between two groups of sender)

```{r}

# average SNS messages received each day from each category of sender, rounded to 1 decimal
avg_count_per_day_from_friends <- entire_day_from_friends %>% mean() %>% round(1)
avg_count_per_day_from_family <- entire_day_from_family %>% mean() %>% round(1)

# value set up for bar graph 3, taking the mean and rounding the number of messages
# received from each group, during each time frame over the entire survey
avg_from_friends_morning <- latest_data$morning_msg_from_friends_acquaintances %>% mean() %>% round(1)
avg_from_friends_midday <- latest_data$midday_msg_from_friends_acquaintances %>% mean() %>% round(1)
avg_from_friends_night <- latest_data$night_msg_from_friends_acquaintances %>% mean() %>% round(1)

avg_from_family_morning <- latest_data$morning_msg_from_family_partner %>% mean() %>% round(1)
avg_from_family_midday <- latest_data$midday_msg_from_family_partner %>% mean() %>% round(1)
avg_from_family_night <- latest_data$night_msg_from_family_partner %>% mean() %>% round(1)

# more set up, aligning the number of elements in each category by multiplying
# them to match them against other variables. Creating a new data frame for
# bar graph 3 in order to explore & compare how two groups of sender do during
# the different time frames of the day.
sender_category <- rep(c("Friends & acquaintances" , "Family & Partner") , 3)
time_frame <- c(rep("Morning", 2), rep("Midday", 2), rep("Night", 2))
average_count <- c(avg_from_friends_morning, 
                   avg_from_family_morning, 
                   avg_from_friends_midday, 
                   avg_from_family_midday, 
                   avg_from_friends_night, 
                   avg_from_family_night)
new_data <- data.frame(sender_category, time_frame, average_count)

# order definition for how the x axis, because the default was to put midday before
# morning under alphabetic ordering.
time_order <- c("Morning", "Midday", "Night")


# bar graph 3 (Summary and comparison for average SNS messages between
# two groups of sender), system assigned color scheme, collapsed and grouped
# bars in the same time frame for readability.
ggplot(new_data, aes(y = average_count, 
                 x = factor(time_frame, level = time_order), 
                 fill = sender_category)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(title = "Sender & frequency SNS message survey average",
       subtitle = "The average number of SNS messages received categorized with time and sender.",
       caption = "Source: Google Form survey",
       x = "Time frames during the day",
       y = "Average no. of SNS msg received")

```

On average, `r avg_count_per_day_from_friends` SNS messages are received each day from friends & acquaintances.

On average, `r avg_count_per_day_from_family` SNS messages are received each day from family & partner.

